\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage{expl3}
\expandafter\def\csname ver@l3regex.sty\endcsname{}

\moderncvstyle{classic}
\moderncvcolor{green}
\nopagenumbers{}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.80]{geometry}
\usepackage{fontawesome5}

\name{Leonardo Lopes}{Pereira}
\title{Back-end Developer}
\phone[mobile]{+55~84~9~8116~1601}
\phone[mobile]{+33~07~69~56~96~98}
\email{leonardolopespereira@outlook.com}
\social[linkedin]{leonardo-lopes-pereira}
\social[github]{llp-devr}

\begin{document}
\makecvtitle{}

\section{Professional Experience}
\cventry{2023 -- Present}{Zup IT}{Back-End Developer}{StackSpot Project}{}{
Delivered and evolved core backend systems for StackSpot’s cloud platform, enabling secure, scalable, and reliable cloud resource management
at enterprise scale. Drove architectural and implementation improvements that reduced infrastructure setup and provisioning time by approximately
70\%, significantly accelerating developer productivity and time-to-market. Played a key role in defining and enforcing backend architecture
standards, ensuring long-term scalability, maintainability, and code quality. Acted as a second-level support reference for critical production
issues, contributing to high platform availability and operational stability. Leveraged Kubernetes and Crossplane for infrastructure orchestration,
with services implemented in Kotlin and Golang, and designed an event-driven architecture using PostgreSQL, DynamoDB, Redis, SQS, and Kafka.
}
\cventry{2020 -- 2023}{AUDITA!}{Co-founder}{Lead Developer}{}{
Co-founded and led the technical execution of a fintech startup focused on automated tax review for Brazilian companies. Architected and built
a data analysis platform that transformed a fully manual tax review process from ~30 days to under 3 hours, unlocking faster insights and
materially improving client cash recovery potential. Owned the end-to-end system design and implementation, balancing performance, accuracy,
and scalability. Employed Rust for high-performance document parsing, Python for large-scale data processing and analytics, and PostgreSQL
as the core data platform.
}

\section{Education}
\cventry{2024 -- Present}{École 42}{Expert en Architecture Numérique}{Paris}{France}{Engaged in a formal qualification program focused on AI and low-level systems programming through hands-on, project-based learning in a collaborative, peer-driven environment.}
\cventry{2015 -- 2017}{UFRN}{Postgraduate Specialist in Tax Law}{Natal}{Brazil}{}
\cventry{2006 -- 2011}{UFRN}{Bachelor of Laws}{Natal}{Brazil}{}

\section{Certification}
\cventry{2024}{AWS}{AWS Certified Developer – Associate}{}{}{}
\cventry{2023}{Python Institute}{PCEP – Certified Entry-Level Python Programmer}{}{}{}

\subsection{Additional Certifications}
\cventry{2026}{C++ Institute}{CLE – C Certified Entry-Level Programmer}{}{}{}
\cventry{2025}{CodinGame}{Kotlin Certification}{}{}{}
\cventry{2025}{CodinGame}{C Certification}{}{}{}
\cventry{2025}{EF SET}{English - C1 Advanced}{}{}{}
\cventry{2024}{Pearson VUE}{English for IT B2 / GSE 59-75}{}{}{}

\section{Skills}
\cvitem{Programming Languages}{C, C++, Go, Kotlin, Python, Rust}
\cvitem{Tools \& Platforms}{AWS, Crossplane, Docker, Git, Kubernetes, Terraform}
\cvitem{Soft Skills}{Effective Communication, Leadership, Team Collaboration, Critical Thinking, Adaptability, Time Management}

\section{Languages}
\cventry{}{Portuguese}{Native}{}{}{}
\cventry{}{English}{C1}{}{}{}
\cventry{}{French}{A1}{}{}{}
\cventry{}{German}{A1}{}{}{}

\end{document}
